---
title: "ANA515 Week 5 Activity"
author: "Jiaxuan Ren"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=TRUE, echo=TRUE}
# Global options that apply to every chunk.
knitr::opts_chunk$set(echo = TRUE, message=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=60))
```

## Description of the data

The [candy-power-ranking](https://github.com/fivethirtyeight/data/tree/master/candy-power-ranking) dataset measures "How often did a fun-sized candy of a given type win its matchups against the rest of the field?" and I hope to use this dataset to answer research question "What Halloween candy people most prefer?"

## Read Data

```{r read_data, include=TRUE}
# Load tidyverse library
library(tidyverse)

# Use read_csv function to read the data "candy-data.csv"
mydata <- read_csv("candy-data.csv")
```

## Clean the data

```{r clean_data, include=TRUE}
# Filter the data to only include top-10 'winpercent' candy and assigned the filtered data into a new object called 'filtered_data'.
filtered_data <- mydata %>% top_n(10, winpercent)
```

## Visualization
### 1. The figure below shows the top-10 candy brands that win the most matchups "How often did a candy win its matchups against the rest?". The dark blue denotes whether the candy is a bar or not (shallow blue).
```{r visual_1, include=TRUE, echo=TRUE}
ggplot(filtered_data, aes(x=winpercent, y=competitorname, fill=bar)) + 
  geom_col() +
  labs(x="Win Percent", y="Candy Brand", title="Candy Preference")
```

### 2. The figure below shows the top-10 candy brands that win the most matchups "How often did a candy win its matchups against the rest?". The y-axis indicates how many percentages of sugar is contained in the candy
```{r visual_2, include=TRUE, echo=TRUE}
ggplot(filtered_data, aes(x=winpercent, y=sugarpercent)) + 
  geom_line() +
  geom_point() +
  labs(x="Win Percent", y="Sugar Percent", title="Candy Preference based on Sugar Percent")
```
